---
title: "Fix Issues In Final geocoding"
author: "Alan Jackson"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)

database <- readRDS("~/Dropbox/CrimeStats/CensusGeoTable_progress.rds")

knitr::opts_chunk$set(echo = TRUE)
```

## Locations mis-identified in wrong city

Most of the South Houston addresses (but not all) should be Houston
Similarly for Bellaire.

Houston police respond to crimes where they are when they see them, so
there are reports that are not in the city. The Beat refers to the office
that the person filing the report works out of, not the beat where the
offense occurred.

For matches outside the city, flag in the status field as "out of city"

```{r flag out of city}

set_redo <- function(df, mask) {
  df[mask,]$lat <- NA
  df[mask,]$long <- NA
  df[mask,]$status <- "fail"
  df[mask,]$geocode_status <- "redo" # redo with match_address
  return(df)
}

# address of form [0-9]+ [NSEW] name suffix , city, state, zip, USA
gethouse <- function(address) {
  x <- unlist(strsplit(unlist(address), " "))
  house_number <- as.numeric(trimws(x[1]))
  return(house_number)
}
#####################################***  run this
# Bellaire
#####################################

mask1 <- grepl("BELLAIRE, TX", database$match_address, ignore.case = TRUE)
database[mask1,]$status    <- "out of city"
mask2 <- grepl("1A|17E|15E|18F", database$Beat, ignore.case = TRUE)
mask <- mask1&mask2
database[mask1,]$status    <- "success"

#####################################
# Baytown
#####################################
#  Main St should really be in Galena Park based on Beat
mask1<- grepl("Baytown, TX", database$match_address, ignore.case = TRUE)
mask2 <- grepl("success", database$status, ignore.case = TRUE)
mask3 <- grepl("s main st", database$match_address, ignore.case = TRUE)
mask <- mask1&mask2&!mask3 # S Main is only HPD address in Baytown
database[mask,]$status    <- "out of city"
mask <- mask1&mask2&mask3 # S Main is only HPD address in Baytown
database[mask,]$match_address    <- str_replace(
                                    database[mask,]$match_address,
                                    "BAYTOWN, TX, 77520",
                                    "GALENA PARK, TX")
database <- set_redo(database, mask)

#####################################
# South Houston
#####################################

#  This is complicated by the fact that the geocoders mistakingly
#  placed some Houston addresses in South Houston
#  For those addresses, zero out the lat/long and set up for a
#  geocoding redo

mask1 <- grepl("South Houston, TX", database$match_address, ignore.case = TRUE)

    #  12th > 799, = W 12th
    #  13th > 799, = W 13th
    #  15th > 699, = W 15th
    #  16th > 1099, = W 16th
    #  4th > 699, = W 4th
    #  7th > 1099, = W 7th
    #  11th > 1099, = W 11th
    #  Dallas with Beat=1A20 = W Dallas

addwest <- function(database, mask, street, number) {
  mask2 <- grepl(street, database$match_address, ignore.case = TRUE)
  mask3 <- as.numeric(str_extract(database$match_address, "\\d+"))>number
  mask3[is.na(mask3)] <- FALSE
  mask <- mask1&mask2&mask3 
  print(sum(mask))
  if (sum(mask) > 0) {
    database[mask,]$Address <- str_replace(database[mask,]$Address,
                                           street,
                                           paste("W", street))
    database[mask,]$geocode_status <- "pending"
  }
  mask <- mask1&mask2&!mask3 
  if (sum(mask) > 0) {
    database[mask,]$status    <- "unknown"
  }
  return(database)
}

database <- addwest(database, mask, "12TH ST", 799)
database <- addwest(database, mask, "13TH ST", 799)
database <- addwest(database, mask, "15TH ST", 699)
database <- addwest(database, mask, "16TH ST", 1099)
database <- addwest(database, mask, "4TH ST", 699)
database <- addwest(database, mask, "7TH ST", 1099)
database <- addwest(database, mask, "11TH ST", 1099)

mask2 <- grepl("Dallas St", database$match_address, ignore.case = TRUE)
mask3 <- grepl("1A20", database$Beat, ignore.case = TRUE)
mask <- mask1&mask2 # retry
database[mask,]$status    <- "fail"
database[mask,]$status    <- "unresolvable" #second time through

database[mask,]$geocode_status    <- "fail"
mask <- mask1&mask2&mask3 # make W Dallas
database[mask,]$Address    <- str_replace(
                                    database[mask,]$Address,
                                    "9 DALLAS",
                                    "9 W DALLAS")

mask2 <- grepl("success", database$status, ignore.case = TRUE)
mask3 <- grepl("pending", database$geocode_status, ignore.case = TRUE)
mask <- mask1&mask2&!mask3 # set the rest to "out of city"
database[mask,]$status    <- "out of city"

#############   end of South Houston

#####################################
# Pasadena
#####################################

# Beats 11H, 9C, and 12D border Pasadena, so these are probably legitimate

mask1 <- grepl("Pasadena, TX", database$match_address, ignore.case = TRUE)
mask2 <- grepl("11H|9C|12D", database$Beat, ignore.case = TRUE)
mask <- mask1&!mask2
database[mask,]$status    <- "out of city"

#####################################
# Deer Park
#####################################

mask1 <- grepl("Deer Park, TX", database$match_address, ignore.case = TRUE)
database[mask1,]$status    <- "out of city"

#####################################
# Porter
#####################################

mask1 <- grepl("Porter, TX", database$match_address, ignore.case = TRUE)
database[mask1,]$status    <- "out of city"

#####################################
# Sugarland
#####################################

# Big one here is mispositioned Hwy-6, which needs extensive rework
# Rename to N Texas 6 and S Texas 6 based on beat

mask1 <- grepl("HWY 6", database$Address, ignore.case = TRUE)
sum(mask1)
mask2 <- grepl("20G|19G30", database$Beat, ignore.case = TRUE)
mask <- mask1&mask2
sum(mask)
database[mask,]$Address    <- str_replace(
                                    database[mask,]$Address,
                                    "HWY 6",
                                    "S TEXAS 6")
database[mask,]$status    <- "fail"
database[mask,]$geocode_status    <- "fail"
mask2 <- grepl("4F30", database$Beat, ignore.case = TRUE)
mask <- mask1&mask2
sum(mask)
database[mask,]$Address    <- str_replace(
                                    database[mask,]$Address,
                                    "HWY 6 N*\\s*",
                                    "N TEXAS 6")
database[mask,]$status    <- "fail"
database[mask,]$geocode_status    <- "fail"

#   Airport Blvd

mask1 <- grepl("W AIRPORT BLVD", database$Address, ignore.case = TRUE)
sum(mask1)
mask2 <- grepl("16E10|15E40|14D|13D|12D", database$Beat, ignore.case = TRUE)
mask <- mask1&mask2
sum(mask)
database[mask,]$Address    <- str_replace(
                                    database[mask,]$Address,
                                    "W AIRPORT BLVD",
                                    "AIRPORT BLVD")
database[mask,]$status    <- "fail"
database[mask,]$geocode_status    <- "fail"

#####################################
# Brookside Village
#####################################

mask1 <- grepl("BROOKSIDE VL, TX", database$match_address, ignore.case = TRUE)
database[mask1,]$status    <- "out of city"







```

##    Save off to file

```{r save}

saveRDS(database, "~/Dropbox/CrimeStats/CensusGeoTable_progress.rds")

```


