---
title: "Make Block Center"
author: "Alan Jackson"
date: "July 13, 2018"
output: html_document
---

```{r setup, include=FALSE}

library(jsonlite)
library(RCurl)
library("tidyverse")
library("stringr") # string tools

options(stringsAsFactors = FALSE)

census_geocoder <- function(address,type,secondary,state){
    addy <- paste("street=",gsub(" ","+",address),sep="")
    if(type=="z"){
          wild <- paste("zip=",gsub(" ","+",secondary),sep="")
        }else{
          wild <- paste("city=",gsub(" ","+",secondary),sep="")
    }
    
    state <- paste("state=",gsub(" ","+",state),sep="") 
    string <-  paste("https://geocoding.geo.census.gov/geocoder/geographies/address?",addy,"&",wild,"&",state,"&benchmark=4&vintage=4&format=json",sep="")
    json_file<-fromJSON(getURL(string))

    #Check if there are results
    if(length(json_file$result$addressMatches)>0){
      
      #If not, kick back an empty dataframe
      if(is.null(json_file$result$addressMatches$coordinates$x[1])==TRUE){
        print("no result")
        return(data.frame(
          address="",
          lat = "",
          lon= "",
          tract = "",
          block = ""))
        
      } else{

        #  Address,lat,lon,tract, block (keep first match)
        address <- as.character(data.frame(json_file$result$addressMatches$matchedAddress)[1,])
        lat <- as.character(json_file$result$addressMatches$coordinates$y[1])
        lon <- as.character(json_file$result$addressMatches$coordinates$x[1])
        tract <- data.frame(json_file$result$addressMatches$geographies$`Census Tracts`)$GEOID[1]
        block <- data.frame(json_file$result$addressMatches$geographies$`2010 Census Blocks`)[1,c("GEOID")]

        return(data.frame(
                address = address,
                lat = lat,
                lon = lon,
                tract = tract,
                block = block))
    
      }
    }
}



knitr::opts_chunk$set(echo = TRUE)
```

## Read in geocoded files

Read in both geocoded files, use best address and add 99 to address, then geocode that address with census tool, average location to get block center, and save to GeocodeMaster.rmd

```{r read in files, merge, and create new addresses}

file1 <- readRDS("~/Dropbox/CrimeStats/Master_Geocode.rds")
file2 <- readRDS("~/Dropbox/CrimeStats/GoogleLocationsMaster.rds")

# New dataframe will have ID, Address, Lat1, Lon1, Lat2, Lon2, NewAddress

ff <- file1 %>%
  mutate(Lat1=as.numeric(strsplit(LatLong,",")[[1]][2]),    
         Lon1=as.numeric(strsplit(LatLong,",")[[1]][1])) %>%
  select(ID, Address=MatchAddress, Lat1, Lon1) %>%
  bind_rows(., 
            select(file2, ID, Address=StreetName, Lat1=lat1, Lon1=lon1) ) %>%
  mutate(Lat2=NA, Lon2=NA) %>%
  mutate(NewAddress=str_replace(Address,"^([0-9]*)00 ", "\\199 "))
  

```

##   Use census geocoder to get lat longs

```{r census geocoding}

## Geocode the addresses


ff$match <- NA
ff$lat <- NA
ff$lon <- NA
ff$tract <- NA
ff$block <- NA

ff$NewAddress <- str_replace(ff$NewAddress, "TX ", "TX, ")

for (i in 77001:nrow(ff)) {
  answer <- NULL
  attempt <- 1
  while( is.null(answer) && attempt <= 3 ) {
    if (attempt>1){print(paste("attempted", attempt))}
    attempt <- attempt + 1
    try(
      answer <- census_geocoder(strsplit(ff$NewAddress[i],",")[[1]][1], "z",
                                strsplit(ff$NewAddress[i],",")[[1]][4], "TX")
    )
  } 
  print(paste(i,":",ff$NewAddress[i], answer[1]))
  if (!is.null(answer) && nchar(answer$address)>0){
    ff$match[i] <- answer[[1]]
    ff$lat[i] <- answer[[2]]
    ff$lon[i] <- answer[[3]]
    ff$tract[i] <- answer[[4]]
    ff$block[i] <- answer[[5]]
  }
  Sys.sleep(1)
  if (i%%1000==0){save.image()}
}

save.image()

saveRDS(ff, file=paste("~/Dropbox/CrimeStats/FinalGeodata.rds",sep=""))

```

##  Take last uncoded addresses and run through google


```{r google geocode}

library(ggmap)
library(stringr)
library(tidyr)
library(dplyr)
library(purrr)

options(stringsAsFactors = FALSE)

#   Empty dataframe for accepting lat long values
latlongs <- data.frame(types=character(),
                       Latitude=numeric(), 
                       Longitude=numeric(), 
                       type=character(),
                       StreetName=character(),
                       LocType=character(),
                       stringsAsFactors=FALSE) 

#   Function for pulling fields out of nested lists returned by geocode
getfields <- function(x){
  if(! is.na(x) && length(x$results)>0)  {data.frame(
    Latitude=as.numeric(x$results[[1]]$geometry$location$lat),
    Longitude=as.numeric(x$results[[1]]$geometry$location$lng),
    types=x$results[[1]]$types[1],
    StreetName=x$results[[1]]$formatted_address,
    LocType=x$results[[1]]$geometry$location_type,
    stringsAsFactors = FALSE)
  } else if ("status" %in% names(x) && x$status=="ZERO_RESULTS"){
    data.frame(types=x$status,Latitude=NA,Longitude=NA, StreetName=NA,LocType=NA,stringsAsFactors = FALSE)
  } else{
    data.frame(types=NA,Latitude=NA,Longitude=NA, StreetName=NA,LocType=NA,stringsAsFactors = FALSE)
  }
}

testgeocode <- function(x){
  if(length(x$results)==0){
    print(paste("--->", x$status))
  }
}

ffnew <- ff[is.na(ff$match),] # grab only rows with no match
ffnew <- ffnew[!duplicated(ffnew$NewAddress),] # get rid of duplicates
#   initialize dfgoogle first time through with new columns
ffnew$type <- NA
ffnew$StreetName <- NA
ffnew$LocType <- NA
#--------------  repeat from here

geocodeQueryCheck()
mask1 <- (is.na(ffnew$lon) | is.na(ffnew$lat))& ((ffnew$type != "ZERO_RESULTS") | is.na(ffnew$type))

sum(mask1)
limit <- min(geocodeQueryCheck(), sum(mask1))
# run geocode for each record up to the daily limit, and then average the lat/long
# values from each end of the block to get a true block center value.
#Addresses <- paste(ffnew$Add1[mask1][1:limit], ffnew$Street[mask1][1:limit])

zero = 0
query = 0
numb = 0
for (i in 1:limit) {
  if (is.na(ffnew$NewAddress[mask1][i])){next}
  print(ffnew$NewAddress[mask1][i])
  AllLatLong <- geocode(ffnew$NewAddress[mask1][i], output="all") # geocode addresses
  numb <- numb + 1
  print(paste("----> ",numb," ",limit-numb))
  #latlongs <- map_df(AllLatLong, getfields) # extract desired fields
  latlongs <- getfields(AllLatLong)
  
  ffnew$lon[mask1][i] = latlongs$Longitude
  ffnew$lat[mask1][i] = latlongs$Latitude
  ffnew$StreetName[mask1][i] = latlongs$StreetName
  ffnew$LocType[mask1][i] = latlongs$LocType
  ffnew$type[mask1][i] = latlongs$types
  
  #testgeocode(AllLatLong)
  if(length(AllLatLong$results)==0){
    print(paste("--->", AllLatLong$status))
    if (AllLatLong$status == "OVER_QUERY_LIMIT") {
      query <- query + 1
    }
    if (AllLatLong$status == "ZERO_RESULTS") {
      zero <- zero + 1
    }
  }
  
  Sys.sleep(2)
}

print(paste("limit =",limit,", Over Query =",query,", Zero =",zero, " Pct fail =",query/limit))
save.image()

#   Save temporary results

saveRDS(ffnew, file="~/Dropbox/CrimeStats/ffnew.rds")

```

##    QC data - look for values outside of area, or where distance between
##    nearby values is large.

```{r QC results}



```

