---
title: "MakeGeocodingFile"
author: "Alan Jackson"
date: "8/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stringr)
library(dplyr)
library(ggmap)
library(rgeos)
library(sf)
library(lwgeom)

googleproj4 <- "+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +wktext  +no_defs"
googlecrs <- 4326

options(stringsAsFactors = FALSE)

geotable <- readRDS("~/Dropbox/CrimeStats/GeoTable_27Aug2019.rds")

generated <- readRDS("~/Dropbox/CrimeStats/Generated_Coordinates.rds")

```

## Make geocoding file

  * blank out generated locations and then add back
   
  * intersect geotable with:
      + zipcode
      + census tract
      + neighborhood
  * clean up status field to be more sensible
  * end up with Address, Beat, Match_address, Lat, Long, Tract. Block, Zip, Neighborhood
     Source (census, google, manual, generated), Status (success, failed, impossible, out of range, outside boundary)
     
  * Make neural net training set (similar but also include raw address)


```{r add generated locations}

#####   check_match
check_match <- function(test_Address, testdata){
    # Did I already succeed at this match somewhere?
    a <- testdata %>% filter(test_Address == Address,
                              status=="success" )
    if (nrow(a)>0){
      return(a)
    } else {return(FALSE)}
}

#   usage:
#   a <- check_match(geotable[i,], previous_match)
#   if (is_tibble(a)) {geotable[i,4:10] <- a[1,4:10]
#      print("found previous match")}

#   fix double blank in generated filend missing blank in geotable

generated$Address <- str_replace(generated$Address, "  ", " ")
geotable$Address <- str_replace(geotable$Address, "n,", "n ,")
geotable$Address <- str_replace(geotable$Address, "9\\([A-Z]\\)", "9 \\1")

# change manual redo to manual (what did I do that for anyway?)

geotable$geocode_status <- str_replace(geotable$geocode_status, "manual redo", "manual")

####   Spin through file and match generated
for (i in begin:nrow(geotable)) {
  
  # first blank out generated data, in case it is bogus
  
  if(geotable[i,]$geocode_status == "generated") {
    geotable[i,]$lat <- NA
    geotable[i,]$long <- NA
    geotable[i,]$geocode_status <- "redo"
    geotable[i,]$status <- "redo"
    print(paste("-- clear -->",geotable[i,]$Address))
    
  }

  if(geotable[i,]$geocode_status!="manual"){ 
    a <- check_match(geotable[i,]$Address, generated)
    if (is_tibble(a)) {
      geotable[i,6:7] <- a[1,2:3]
      geotable[i,]$geocode_status <- "generated"
      geotable[i,]$status <- "success"
      print(paste("-- update -->",geotable[i,]$Address))
      next
    }
  }
}

####   Spin through file and match against self
for (i in begin:nrow(geotable)) {
  
  if(grepl("redo", geotable[i,]$geocode_status)){ 
    a <- check_match(geotable[i,]$Address, geotable)
    if (is_tibble(a)) {
      geotable[i,4:10] <- a[1,4:10]
      print(paste("-- update -->",geotable[i,]$Address))
      next
    }
  }
}


# summary of some fields

sort(unique(geotable$geocode_status))
sort(unique(geotable$status))

# Save file

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_22Aug2019_withgen.rds")

####   mask out rows with bad coordinates
maskcoord <- !(is.na(geotable$lat) | is.na(geotable$long))
sum(maskcoord)
#maskcoord <- maskcoord & !grepl("fail", geotable$geocode_status)
maskcoord <- maskcoord & grepl("success", geotable$status)
sum(maskcoord)
#  Create a temporary sf data frame for doing the intersects
# set longitudes as the first column and latitudes as the second
dat <- data.frame(Longitude=geotable$long[maskcoord], Latitude=geotable$lat[maskcoord], Address=geotable$Address[maskcoord], stringsAsFactors = FALSE)

dat <- st_as_sf(dat, coords=c("Longitude", "Latitude"), crs=googlecrs, agr = "identity")

```

## Intersect geotable with zipcodes

Read in a file of local zipcode boundaries and intersect with
geotable, and add the zip code to the table.


```{r zipcodes}

# read in previously created zipcode polygon file

ziplatlong <- readRDS("~/Dropbox/CrimeStats/ZipCodes.rds")

#   find points in polygons
#   since zipcodes don't overlap, let's just grab the array index
#   instead of creating a huge matrix
a <- st_intersects(dat, ziplatlong, sparse = TRUE)

#   Append the ZIP field to the data frame
geotable$Zip_Code[maskcoord] <- ziplatlong$Zip_Code[unlist(a)]

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_22Aug2019.rds")
```

## Add census tract and block

Use previously generated dataset with census blocks


```{r census tract}

# polygons for Harris and surrounding counties
CensusHou <- readRDS("~/Dropbox/CrimeStats/HouCensusPolys.rds")

#   look for problems
sum(!st_is_valid(CensusHou))
#   find points in polygons
a <- st_intersects(dat, CensusHou, sparse = TRUE)
badpoints <- grep(" ",a) # bad points where apparently census blocks overlap
d <- CensusHou %>% select(NAME10)
plot(d[unlist(a[badpoints[7]]),], axes=TRUE, key.pos=NULL)

for (i in 1:length(badpoints)) {
  a[[badpoints[i]]] <- a[[badpoints[i]]][1]
}
# Find and fix points where there was a miss
idx <- !(sapply(a, length)) # where are they?
sum(idx)
a[idx] <- NA
#   add county, census tract and block number to data
geotable$CountyFIP[maskcoord] <- CensusHou$COUNTYFP10[unlist(a)]
geotable$CensusTract[maskcoord] <- CensusHou$TRACTCE10[unlist(a)]
geotable$CensusBlock[maskcoord] <- CensusHou$BLOCKCE10[unlist(a)]

# Do the new blocks match the old ones?

temp <- 
geotable %>% 
  filter(!is.na(block)) %>% 
  filter(geocode_status=="census") %>% 
  filter(block != CensusBlock) %>% 
  select(Address, Beat, n, lat, long, tract, block, CountyFIP, CensusTract, CensusBlock)

#############################
#####   save GeoTable   #####
#############################

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_23Aug2019.rds")

```

##   add neighborhood field

```{r neighborhood}

#   Read cleaned neighborhood polygon file

nbhd <- readRDS("~/Dropbox/CrimeStats/NeighborhoodPolys.rds")

#   collect all the neighborhoods a point falls into, make a list,
#   and put into the Nbhd field

# st_intersects to see if points are inside poly
#  This is a matrix of T/F values, npoints x npolys in size
#  if a point is in multiple polys it will show up here
a <- st_intersects(dat, nbhd, sparse = FALSE)
max(rowSums(a)) # this is the maximum number of polys for some point
hist(rowSums(a))# just curious how they are distributed.

diddle <- function (i) {nbhd$Name[i]}

geotable$Wikimapia_Nbhd[maskcoord] <-  apply(a,1,diddle)  #  work on "a" row-wise

#   Clean up unknown neighborhoods and clarify what we are using

geotable$Wikimapia_Nbhd[geotable$Wikimapia_Nbhd=="character(0)"] <- NA

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_23Aug2019.rds")

```

##  add super neighborhoods

```{r super neighborhoods}

temp <- readRDS("~/Dropbox/CrimeStats/SuperNeighborhoodPolys.rds")
#   find points in polygons
#   since superneighborhoods don't overlap, let's just grab the array index
#   instead of creating a huge matrix
a <- st_intersects(dat, temp, sparse = TRUE)

# Replace empty values with 89
a <- unlist(replace(a, !sapply(a, length),89))
# Now add super neighborhood 89 as NA
temp[89,] <- temp[88,]
temp$SNBNAME[89] <- NA

#   Append the super neighborhood field to the data frame
geotable$SuperNeighborhood[maskcoord] <- temp$SNBNAME[a]

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_23Aug2019.rds")
```

##  fix some errors

```{r repair}

make_success <- function(address, status) {
  mask <- grepl(address, geotable$Address, ignore.case = TRUE)
  print(sum(mask))
  geotable[mask,]$status  <- status
  geotable
}

make_no_census <- function(address, status) {
  mask1 <- grepl(address, geotable$Address, ignore.case = TRUE)
  mask2 <- is.na(geotable$CensusTract)
  mask <- mask1 & mask2
  print(sum(mask))
  geotable[mask,]$status  <- status
  geotable
}

geotable <- make_success("ROCKLEY RD", "success")
geotable <- make_success("MILL VALLEY RD", "success")
geotable <- make_success("PLEASANT VALLEY RD", "success")
geotable <- make_success("MAPLE VALLEY RD", "success")
geotable <- make_success("WILD VALLEY RD", "success")
geotable <- make_success("FARLEY RD", "success")
geotable <- make_success("SPRING VALLEY RD", "redo")
geotable <- make_success("LANGLEY RD", "success")
geotable <- make_no_census("MYKAWA RD", "outside city")
geotable <- make_no_census("ST EMANUEL ST", "bad street number")
geotable <- make_success("3899 ST EMANUEL ST", "success")
geotable <- make_success("ST EMANUEL ,", "redo")
geotable <- make_success("WILEY RD", "success")
geotable <- make_success("2699 RUSTIC WOODS DR", "success")
geotable <- make_success("2799 RUSTIC WOODS DR", "success")
geotable <- make_success("22699 RUSTIC WOODS DR", "bad street number")

geotable <- make_success("TANGLEY RD", "redo")
geotable$Address <- str_replace(geotable$Address, "TANGLEY RD", "TANGLEY")

geotable$Address <- str_replace(geotable$Address, "WESTPLACE ,", "WESTPLACE DR ,")
geotable <- make_success("8299 WESTPLACE DR", "bad street number")

geotable$Address <- str_replace(geotable$Address, "MELROSE PARK PL", "MELROSE PARK RD")

geotable$Address <- str_replace(geotable$Address, "DUBOIS", "DU BOIS")
geotable$Address <- str_replace(geotable$Address, "DU BOIS RD", "DU BOIS ST")
geotable$Address <- str_replace(geotable$Address, "DU BOIS ,", "DU BOIS ST ,")
geotable <- make_success("DU BOIS ST", "redo")

geotable <- make_success("ROLGUM", "redo")
geotable$Address <- str_replace(geotable$Address, "ROLGUM PL", "ROLGOM PL CT")

geotable <- make_success("YORKBROOK", "redo")
geotable$Address <- str_replace(geotable$Address, "YORKBROOK", "YORK BROOK DR")

geotable <- make_success("BLUESTEAM ST", "redo")
geotable$Address <- str_replace(geotable$Address, "BLUESTEAM", "BLUESTEM")

geotable <- make_success("BLUESTONE ,", "redo")
geotable$Address <- str_replace(geotable$Address, "BLUESTONE ,", "BLUESTONE DR ,")

geotable <- make_success("VAN CLEVE ,", "redo")

geotable$Address <- str_replace(geotable$Address, "JORDON", "JORDAN")
geotable <- make_success("JORDAN OAKS ,", "redo")

geotable <- make_success("COSTA RICA ,", "redo")
geotable$Address <- str_replace(geotable$Address, "COSTA RICA ,", "COSTA RICA RD ,")

geotable <- make_success("SUNNYVALE", "redo")
geotable$Address <- str_replace(geotable$Address, "SUNNYVALE", "SUNNY VALE")

geotable <- make_success("HOLTKAMP", "redo")
geotable$Address <- str_replace(geotable$Address, "HOLTKAMP", "HOLTCAMP")

geotable <- make_success("GREEN HOOD", "redo")
geotable$Address <- str_replace(geotable$Address, "GREEN HOOD", "GREENHURST")
geotable$Address <- str_replace(geotable$Address, "GREENHURST ,", "GREENHURST ST ,")

geotable <- make_success("OHIO", "redo")
geotable$Address <- str_replace(geotable$Address, "OHIO ST", "OHIO")

geotable <- make_success("BELLACHE", "redo")
geotable$Address <- str_replace(geotable$Address, "BELLACHE", "BELLA NOCHE")

mask1 <- grepl("INTERCONTINENTAL AIRPORT", geotable$RawAddress)
sum(mask1)
mask2 <- grepl("2800-2899 N TERMINAL RD , Houston , TX", geotable$Address)
sum(mask2)
mask <- mask1&!mask2
geotable$Address[mask] <- "2800-2899 N TERMINAL RD , Houston , TX"
geotable$status[mask] <- "redo"

geotable <- make_success("199 FOREST CENTER DR", "success")

geotable <- make_no_census("ELDRIDGE PKWY", "rework")
geotable <- make_no_census("ELDRIDGE RD", "rework")
geotable <- make_no_census("WEST ENGLAND COURT", "redo")
geotable$Address <- str_replace(geotable$Address, "STONE PARK LN", "STONE PARK RD")
geotable <- make_success("KEATS ST", "success")
geotable$Address <- str_replace(geotable$Address, "KEATS ST", "KEATS AVE")
geotable <- make_no_census("AEROPARK DR", "redo")

geotable$Address <- str_replace(geotable$Address, "2351 RD", "2351")
geotable$Address <- str_replace(geotable$Address, "98 W", "99 W")
geotable <- make_success("2799 W BAY AREA BLVD", "outside city")
geotable$Address <- str_replace(geotable$Address, " W PARK $", " W PARK AT SHADY VILLA , Houston , TX")
geotable <- make_no_census("W PARK AT SHADY", "rework")
geotable <- make_no_census("W PARK VIEW", "rework")
geotable$Address <- str_replace(geotable$Address, "PKWT", "PKWY")

mask1 <- grepl("S LOOP E FWY", geotable$Address)
sum(mask1)
mask2 <- grepl("redo", geotable$status)
sum(mask2)
mask <- mask1&mask2
sum(mask)
geotable$Address[mask] <- str_replace(geotable$Address[mask], "E FWY", "W FWY")

mask <- grepl("NORTH FWY", geotable$Address)
sum(mask)
geotable$status[mask] <- str_replace(geotable$status[mask], "redo", "bad street number")

mask <- grepl("FWY", geotable$Address)
sum(mask)
geotable$status[mask] <- str_replace(geotable$status[mask], "redo", "bad street number")

mask <- grepl("PKWY", geotable$Address)
sum(mask)
geotable$status[mask] <- str_replace(geotable$status[mask], "redo", "bad street number")

mask <- grepl("BELLFORT", geotable$Address)
sum(mask)
geotable$status[mask] <- str_replace(geotable$status[mask], "redo", "bad street number")

mask <- grepl("OREM", geotable$Address)
sum(mask)
geotable$status[mask] <- str_replace(geotable$status[mask], "redo", "bad street number")

mask1 <- grepl("DU BOIS", geotable$Address)
mask2 <- grepl("6800|6900", geotable$Address)
mask <- mask1&mask2
sum(mask)
geotable$Address[mask] <- str_replace(geotable$Address[mask], "ST", "RD")

geotable$Address <- str_replace(geotable$Address, "VAN CLEVE", "VAN CLEVE ST")
geotable$Address <- str_replace(geotable$Address, "JORDAN OAKS", "JORDAN OAKS ST")
geotable$Address <- str_replace(geotable$Address, "ST EMANUEL ,", "ST EMANUEL ST ,")

#   column screwup repair
mask <- grepl("[9]", geotable$status)
sum(mask)
geotable$lat[mask] <- geotable$block[mask]
geotable$long[mask] <- geotable$status[mask]
geotable$geocode_status[mask] <- "generated"
geotable$match_address[mask] <-  paste0(as.character(as.numeric(str_extract(
                                 geotable$Address[mask],"\\d*"))+50),
                                 str_remove(geotable$Address[mask],"\\d+-\\d+"))
geotable$tract[mask] <- NA
geotable$block[mask] <- NA
geotable$status[mask] <- "success"

saveRDS(geotable,"~/Dropbox/CrimeStats/GeoTable_28Aug2019.rds")
```

```{r manual}
###############   special case function
special_case <- function(mydf, mask, address, lat, long){
  if (sum(mask)>0){
    print(paste(sum(mask), "records changed"))
    mydf[mask,]$match_address <- address
    mydf[mask,]$status    <- "success"
    mydf[mask,]$geocode_status    <- "manual redo"
    mydf[mask,]$lat    <- lat
    mydf[mask,]$long   <- long
    mydf[mask,]$GType    <- "RANGE_INTERPOLATED manual"
  }
  return(mydf)
}
#################

specific <- tribble(
  ~block, ~street, ~number, ~lat, ~long, ~zip,
  "9900-9999", "MACE", "9950", 29.621963, -95.220771, "Houston, TX 77034",
  "1800-1899", "DOWLING", "1850", 29.743404, -95.357923, "Houston, TX 77003",
  "3800-3899", "CUMMINS GREEN ST", "3850", 29.730112, -95.440274, "Houston, TX 77046",
  "8400-8499", "WILLOW PL DR S", "8450", 29.959705, -95.557256, "Houston, TX 77070",
  "100-199", "NORTHPINES DR", "150", 30.065324, -95.246784, "Houston, TX 77339",
  "14400-14499", "STONE PARK LN", "14450", 29.613147, -95.496907, "Houston, TX 77339",
  "14400-14499", "HEATHROW FOREST PKWY", "14450", 29.926167, -95.328708, "Houston, TX 77032",
  "0-99", "ALLEN PKWY", "50", 29.758732, -95.371485, "Houston, TX 77002",
  "700-799", "S MAYDE CREEK DR", "750", 29.778621, -95.624493, "Houston, TX 77079",
  "3100-3199", "FM 2351", "3150", 29.568980, -95.169558, "WEBSTER, TX 77598",
  "3200-3299", "FM 2351", "3250", 29.568159, -95.170341, "WEBSTER, TX 77598",
  "3900-3999", "FM 2351", "3950", 29.558509, -95.178667, "WEBSTER, TX 77598",
  "10900-10999", "GREENBEND BLVD", "10950", 29.940254, -95.427968, "Houston, TX 77567",
  "12600-12699", "RODEO SQUARE DR", "12650", 29.706075, -95.606461, "Houston, TX 77072",
  "200-299", "W BAY AREA BLVD", "250", 29.547423, -95.130404, "Houston, TX 77598",
  "1700-1799", "W BAY AREA BLVD", "1750", 29.537674, -95.153514, "Houston, TX 77546",
  "1800-1899", "W BAY AREA BLVD", "1850", 29.537385, -95.154984, "Houston, TX 77546",
  "6800-6899", "DU BOIS RD", "6850", 29.862053, -95.451543, "Houston, TX 77091",
  "6900-6999", "DU BOIS RD", "6950", 29.862722, -95.451561, "Houston, TX 77091",
  "4900-4999", "AEROPARK DR", "4950", 29.934990, -95.315720, "Houston, TX 77032",
  "5200-5299", "AEROPARK DR", "5250", 29.934957, -95.313998, "Houston, TX 77032",
  "19400-19499", "YORK BROOK DR", "19450", 29.540134, -95.153239, "Houston, TX 77546",
  "2100-2199", "VAN CLEVE ST", "2150", 29.612056, -95.390365, "Houston, TX 77047",
  "2200-2299", "VAN CLEVE ST", "2250", 29.612075, -95.389222, "Houston, TX 77047",
  "15100-15199", "JORDAN OAKS ST", "15150", 29.606625, -95.467391, "Houston, TX 77053",
  "5300-5399", "COSTA RICA RD", "5350", 29.836857, -95.47084, "Houston, TX 77092",
  "3200-3299", "SUNNY VALE DR", "3250", 30.062019, -95.169449, "Houston, TX 77345",
  "6400-6499", "BELLA NOCHE DR", "6450", 30.077483, -95.522487, "Houston, TX 77379",
  "800-899", "ST EMANUEL ST", "850", 29.75250,	-95.35448, "Houston, TX 77003",
  "12100-12199", "MELROSE PARK RD", "12150", 29.876002, -95.373002, "Houston, TX 77037",
  "12200-12299", "MELROSE PARK RD", "12250", 29.876937, -95.373018, "Houston, TX 77037"
)

for (i in 1:nrow(specific)) {
  mask <- grepl(paste(specific[i,]$block, specific[i,]$street), 
                geotable$Address, ignore.case=TRUE)
  print(paste(specific[i,]$street, sum(mask)))
  geotable <- special_case(geotable, 
                   mask, 
                   paste0(specific[i,]$number, " ", 
                          specific[i,]$street, ", ",
                          specific[i,]$zip),
                  specific[i,]$lat, 
                  specific[i,]$long 
                   )
}


```


##  clean up

Status field will end up being:

* success - good address, good laocation (so far as I know)
* impossible - not an address, e.g., PO Box or so badly mangled resolution is impossible
* bad street number - street number out of range of possible, or street name bad
* outside city - good address but not in city. Maybe not in state!
* rework - address is probably recoverable but needs future manual effort

```{r clean up}

#   Clean up status field
#       (success, failed, impossible, bad street number, outside city)

geotable$status <- str_replace(geotable$status, "address out of range", "bad street number")
geotable$status <- str_replace(geotable$status, "Road only, street number ignored", "bad street number")
geotable$status <- str_replace(geotable$status, "City only, street ignored", "bad street number")

mask <- grepl("Distance", geotable$status)
sum(mask)
geotable$status[mask] <- "rework"

mask <- grepl("BOX", geotable$Address)
sum(mask)
geotable$status[mask] <- "impossible"
mask <- grepl("fail", geotable$status)
sum(mask)
geotable$status[mask] <- "impossible"

geotable$status <- str_replace(geotable$status, "no result", "bad street number")
geotable$status <- str_replace(geotable$status, "Not an address", "impossible")
geotable$status <- str_replace(geotable$status, "boundary", "city")

sort(unique(geotable$status))
sort(unique(geotable$geocode_status))
```





