---
title: "MakeGeocodingFile"
author: "Alan Jackson"
date: "8/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stringr)
library(dplyr)
library(ggmap)
library(rgeos)
library(sf)
library(lwgeom)

googleproj4 <- "+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +wktext  +no_defs"
googlecrs <- 4326

options(stringsAsFactors = FALSE)

geotable <- readRDS("~/Dropbox/CrimeStats/GeoTable_19Aug2019.rds")

generated <- readRDS("~/Dropbox/CrimeStats/Generated_Coordinates.rds")

```

## Make geocoding file

  * blank out generated locations and then add back
   
  * intersect geotable with:
      + zipcode
      + census tract
      + neighborhood
  * clean up status field to be more sensible
  * end up with Address, Beat, Match_address, Lat, Long, Tract. Block, Zip, Neighborhood
     Source (census, google, manual, generated), Status (success, failed, impossible, out of range, outside boundary)
     
  * Make neural net training set (similar but also include raw address)


```{r add generated locations}

#####   check_match
check_match <- function(test_Address, testdata){
    # Did I already succeed at this match somewhere?
    a <- testdata %>% filter(test_Address == Address,
                              status=="success" )
    if (nrow(a)>0){
      return(a)
    } else {return(FALSE)}
}

#   usage:
#   a <- check_match(geotable[i,], previous_match)
#   if (is_tibble(a)) {geotable[i,4:10] <- a[1,4:10]
#      print("found previous match")}

#   fix double blank in generated filend missing blank in geotable

generated$Address <- str_replace(generated$Address, "  ", " ")
geotable$Address <- str_replace(geotable$Address, "n,", "n ,")
geotable$Address <- str_replace(geotable$Address, "9\\([A-Z]\\)", "9 \\1")

# change manual redo to manual (what did I do that for anyway?)

geotable$geocode_status <- str_replace(geotable$geocode_status, "manual redo", "manual")

####   Spin through file and match generated
for (i in begin:nrow(geotable)) {
  
  # first blank out generated data, in case it is bogus
  
  if(geotable[i,]$geocode_status == "generated") {
    geotable[i,]$lat <- NA
    geotable[i,]$long <- NA
    geotable[i,]$geocode_status <- "redo"
    geotable[i,]$status <- "redo"
    print(paste("-- clear -->",geotable[i,]$Address))
    
  }

  if(geotable[i,]$geocode_status!="manual"){ 
    a <- check_match(geotable[i,]$Address, generated)
    if (is_tibble(a)) {
      geotable[i,6:7] <- a[1,2:3]
      geotable[i,]$geocode_status <- "generated"
      geotable[i,]$status <- "success"
      print(paste("-- update -->",geotable[i,]$Address))
      next
    }
  }
}

####   Spin through file and match against self
for (i in begin:nrow(geotable)) {
  
  if(grepl("redo", geotable[i,]$geocode_status)){ 
    a <- check_match(geotable[i,]$Address, geotable)
    if (is_tibble(a)) {
      geotable[i,4:10] <- a[1,4:10]
      print(paste("-- update -->",geotable[i,]$Address))
      next
    }
  }
}


# summary of some fields

sort(unique(geotable$geocode_status))
sort(unique(geotable$status))

# Save file

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_22Aug2019_withgen.rds")

####   mask out rows with bad coordinates
maskcoord <- !(is.na(geotable$lat) | is.na(geotable$long))
sum(maskcoord)
maskcoord <- maskcoord & !grepl("fail", geotable$geocode_status)
sum(maskcoord)
#  Create a temporary sf data frame for doing the intersects
# set longitudes as the first column and latitudes as the second
dat <- data.frame(Longitude=geotable$long[maskcoord], Latitude=geotable$lat[maskcoord], Address=geotable$Address[maskcoord], stringsAsFactors = FALSE)

dat <- st_as_sf(dat, coords=c("Longitude", "Latitude"), crs=googlecrs, agr = "identity")

```

## Intersect geotable with zipcodes

Read in a file of local zipcode boundaries and intersect with
geotable, and add the zip code to the table.


```{r zipcodes}

# read in previously created zipcode polygon file

ziplatlong <- readRDS("~/Dropbox/CrimeStats/ZipCodes.rds")

#   find points in polygons
#   since zipcodes don't overlap, let's just grab the array index
#   instead of creating a huge matrix
a <- st_intersects(dat, ziplatlong, sparse = TRUE)

#   Append the ZIP field to the data frame
geotable$Zip_Code[maskcoord] <- ziplatlong$Zip_Code[unlist(a)]

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_22Aug2019.rds")
```

## Add census tract and block

Use previously generated dataset with census blocks


```{r census tract}

# polygons for Harris and surrounding counties
CensusHou <- readRDS("~/Dropbox/CrimeStats/HouCensusPolys.rds")

#   look for problems
sum(!st_is_valid(CensusHou))
#   find points in polygons
a <- st_intersects(dat, CensusHou, sparse = TRUE)
badpoints <- grep(" ",a) # bad points where apparently census blocks overlap
d <- CensusHou %>% select(NAME10)
plot(d[unlist(a[badpoints[7]]),], axes=TRUE, key.pos=NULL)

for (i in 1:length(badpoints)) {
  a[[badpoints[i]]] <- a[[badpoints[i]]][1]
}
# Find and fix points where there was a miss
idx <- !(sapply(a, length)) # where are they?
sum(idx)
a[idx] <- NA
#   add county, census tract and block number to data
geotable$CountyFIP[maskcoord] <- CensusHou$COUNTYFP10[unlist(a)]
geotable$CensusTract[maskcoord] <- CensusHou$TRACTCE10[unlist(a)]
geotable$CensusBlock[maskcoord] <- CensusHou$BLOCKCE10[unlist(a)]

# Do the new blocks match the old ones?

temp <- 
geotable %>% 
  filter(!is.na(block)) %>% 
  filter(geocode_status=="census") %>% 
  filter(block != CensusBlock) %>% 
  select(Address, Beat, n, lat, long, tract, block, CountyFIP, CensusTract, CensusBlock)

#############################
#####   save GeoTable   #####
#############################

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_23Aug2019.rds")

```

##   add neighborhood field

```{r neighborhood}

#   Read cleaned neighborhood polygon file

nbhd <- readRDS("~/Dropbox/CrimeStats/NeighborhoodPolys.rds")

#   collect all the neighborhoods a point falls into, make a list,
#   and put into the Nbhd field

# st_intersects to see if points are inside poly
#  This is a matrix of T/F values, npoints x npolys in size
#  if a point is in multiple polys it will show up here
a <- st_intersects(dat, nbhd, sparse = FALSE)
max(rowSums(a)) # this is the maximum number of polys for some point
hist(rowSums(a))# just curious how they are distributed.

diddle <- function (i) {nbhd$Name[i]}

geotable$Nbhd[maskcoord] <-  apply(a,1,diddle)  #  work on "a" row-wise

#   Clean up unknown neighborhoods and clarify what we are using

geotable$Nbhd[geotable$Nbhd=="character(0)"] <- NA

names(geotable)[names(geotable) == 'Nbhd'] <- 'Wikimapia_Nbhd'

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_23Aug2019.rds")

```

##  add super neighborhoods

```{r super neighborhoods}

temp <- readRDS("~/Dropbox/CrimeStats/SuperNeighborhoodPolys.rds")
#   find points in polygons
#   since superneighborhoods don't overlap, let's just grab the array index
#   instead of creating a huge matrix
a <- st_intersects(dat, temp, sparse = TRUE)

# Replace empty values with 89
a <- unlist(replace(a, !sapply(a, length),89))
# Now add super neighborhood 89 as NA
temp[89,] <- temp[88,]
temp$SNBNAME[89] <- NA

#   Append the super neighborhood field to the data frame
geotable$SuperNeighborhood[maskcoord] <- temp$SNBNAME[a]

saveRDS(geotable, "~/Dropbox/CrimeStats/GeoTable_temp_23Aug2019.rds")
```




