---
title: "ReCreate Geocode File"
author: "Alan Jackson"
date: "December 22, 2018"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(stringr)
library(dplyr)

options(stringsAsFactors = FALSE)

reclean <- c("District1aReCleanData.rds", 
             "District2aReCleanData.rds")
recleanpath <- "~/Dropbox/CrimeStats/"

dflist <- vector(mode = "list", length = 2)
for (i in 1:2) {
    dflist[[i]] <- readRDS(paste0(recleanpath, reclean[i]))
}

knitr::opts_chunk$set(echo = TRUE)
```
Call sequence is

* address (required): street number and street name (1234 N Main ST)
* city (optional): City name. If both city and zip are given, they may conflict.
* state (optional): State 2-letter postal abbreviation
* zip (optional): 5 digit US Postal Zipcode

Either city and state, or zip is required

Will return the last match if there are multiple matches. That way downtown Houston will not show up as "Clutch City".

Returns will be:

* status code: 
  + "success"=success 
  + "multiples"=success but multiple answers
  + "partial match"=success but not a 100% match with input address 
  + "fail"=fail
* matching address
* lat
* long
* tract
* block

```{r geocoder}

GetResult <- function(urlreq) {
  #  required libraries 
  
  require(httr)
  
  #   set up to retry twice on server type error (which usually works)
  attempt <- 1
  result <- data.frame(status_code=0)
  while(result$status_code!=200 && attempt<=3 ) {
    if (attempt>1){print(paste("attempted", attempt))}
    attempt <- attempt + 1
    try(
      #     Go get result
      result <- httr::GET(urlreq)
    )
  }
  return(result)
}

Census_decoder <- function(address, city=NA, state=NA, zip=NA){
 
  
  urlreq <- paste0("https://geocoding.geo.census.gov/geocoder/geographies/address?street=",gsub(" ", "+",address))
  if (!is.na(city)){urlreq <- paste0(urlreq,"&city=", city)}
  if (!is.na(state)){urlreq <- paste0(urlreq,"&state=", state)}
  if (!is.na(zip)){urlreq <- paste0(urlreq,"&zip=", zip)}
  urlreq <- paste0(urlreq,"&benchmark=Public_AR_Current&vintage=Current_Current&format=json")
  
  print(urlreq)
  result <- GetResult(urlreq)
  #     did we succeed?
  if (result$status_code != 200) { # failure
    print("+1+>")
    return(data.frame(
      status="fail_code",
      match_address=NA,
      lat=NA,
      long=NA,
      tract=NA,
      block=NA,
      stringsAsFactors = FALSE
    ))
  } else {
  result <- httr::content(result)
  Num_matches <- length(result[["result"]][["addressMatches"]])
  
  if (Num_matches <= 0) { # failed to find address
    print("+2+>")
    return(data.frame(
      status="fail_length",
      match_address=NA,
      lat=NA,
      long=NA,
      tract=NA,
      block=NA,
      stringsAsFactors = FALSE
    ))
  }
    
    # pick matching result if multiples offered
  for (i in 1:Num_matches) {
    temp <- result[["result"]][["addressMatches"]][[i]]
    if (address == 
        str_split(temp[["matchedAddress"]], ",")[1]) { break }
  }
    temp <- result[["result"]][["addressMatches"]][[Num_matches]]
    tract <- temp[["geographies"]][["2010 Census Blocks"]][[1]][["TRACT"]]
    if (is.null(tract)){
      print("+3+>")
      return(data.frame(
        status="fail_tract",
        match_address=NA,
        lat=NA,
        long=NA,
        tract=NA,
        block=NA,
        stringsAsFactors = FALSE
      ))
    }
    status <- "success"
    #####   debug
    match_address=temp[["matchedAddress"]] 
    lat=temp[["coordinates"]][["y"]]
    lon=temp[["coordinates"]][["x"]]
    tract=temp[["geographies"]][["2010 Census Blocks"]][[1]][["TRACT"]]
    block=temp[["geographies"]][["2010 Census Blocks"]][[1]][["BLOCK"]]
    print(paste("+4+>",status, match_address, lat,lon,tract,block))
    #####  end debug
    
    return(data.frame(
      status=status,
      match_address=match_address,
      lat=lat,
      lon=lon,
      tract= tract,
      block=block,
      stringsAsFactors=FALSE
    ))
  } # end if/else
}
```

## Pull coordinates from old geocoding files

Pull old coordinates and attach to ReClean files


```{r oldgeocode}

# get old geotable

oldgeotable <- readRDS("~/Dropbox/CrimeStats/GeoTable.rds")

# Read in clean data files

df <- dplyr::bind_rows(dflist)

# join geotable to reclean files

  # first create address in df: 
  # Block_Range + Suffix + Street + Type + ", Houston, TX"

df$Address <- paste(df$Block_Range, df$Suffix, df$Street, df$Type, ", Houston, TX")
df$Address <- str_replace_all(df$Address, "- ", "")
df$Address <- str_replace_all(df$Address, "  ", " ")

df <- dplyr::left_join(df, oldgeotable, by="Address")

# pull out records not matched or matchable

unmatched <- df %>%
  filter(is.na(GoogleName)) %>%
  filter(!grepl("^UNK", Block_Range.x)) %>%
  filter(!grepl(" NA ", Address)) %>%
  select(Address, Beat) %>%
  distinct() %>%
  filter(!grepl("^UNK", Address)) 

newgeotable <- readRDS("~/Dropbox/CrimeStats/CensusGeoTable.rds")
newgeotable <- newgeotable %>% rename(Address=oldaddress)
df <- dplyr::left_join(unmatched, newgeotable, by="Address")
lastunmatched <- df %>%
  filter(is.na(distance)) %>%
  select(Address, Beat) 

BeatToZip <- readRDS("~/Rprojects/CrimeStats/BeatToZip.rds")

```

##  Census Geocoding

Call census geocoder for first and last address, and on success
average the two answers and add in the lat long values as well as other good stuff.

```{r do geocoding}

getlatlong <- function(addr, beat){
  x <- unlist(strsplit(addr, ","))
  city <- trimws(x[2])
  state <- trimws(x[3])
  adr1 <- unlist(strsplit(str_extract(x[1], "^[0-9]+-[0-9]+"),"-"))[1]
  if (adr1=="0") {adr1 <- "1"} # census dislikes address of zero
  adr1 <- str_replace(adr1, "0$", "1")# dislikes address ending in 0
  adr2 <- unlist(strsplit(str_extract(x[1], "^[0-9]+-[0-9]+"),"-"))[2]
  street <- trimws(sub("^[0-9]+-[0-9]+", "", x[1]))
  
  # Pull list of potential zipcodes
  print("+++++ 1 ++++++")
  ziplist <- BeatToZip[BeatToZip$beat==beat,][2]
  print("+++++ 2 ++++++")
    
  # walk away from end of block if necessary to get a hit
  for (zip in unlist(ziplist)) {
  print("+++++ 3 ++++++")
    loc1 <- Census_decoder(paste(adr1, street), city, state, zip)
  print("+++++ 4 ++++++")
    j=0
    while (loc1[1] != "success" && j<=2) {
      adr1 <- as.character(as.numeric((adr1))+5)
      loc1 <- Census_decoder(paste(adr1, street), city, state, zip)
      j=j+1
    }
    loc2 <- Census_decoder(paste(adr2, street), city, state, zip)
    j=0
    while (loc2[1] != "success" && j<=2) {
      adr2 <- as.character(as.numeric((adr2))-5)
      loc2 <- Census_decoder(paste(adr2, street), city, state, zip)
      j=j+1
    }
  }
  # If both succeed, then return average location. If either fails,
  # return failure. Also check directional prefix
  
  if (loc1[1]!="success" || loc2[1]!="success") {
    print("failure 1")
    return(data.frame(
      status="fail",
      match_address=NA,
      lat=NA,
      long=NA,
      tract=NA,
      block=NA,
      distance=NA,
      stringsAsFactors = FALSE
    ))
  }
  
  #   does the new street match the old street?
  
  x <- unlist(strsplit(loc1$match_address, ","))
  newstreet1 <- trimws(sub("^[0-9]+", "", x[1]))
  x <- unlist(strsplit(loc2$match_address, ","))
  newstreet2 <- trimws(sub("^[0-9]+", "", x[1]))
  #print(newstreet)
  ##if (street != newstreet1 && street != newstreet2) {
    # try adding a bogus zipcode to force it to look at alternatives
   ## loc1 <- Census_decoder(paste(adr1, street), city, zip="77000")
    ##loc2 <- Census_decoder(paste(adr2, street), city, zip="77000")
   ## x <- unlist(strsplit(loc1$match_address, ","))
    ##newstreet1 <- trimws(sub("^[0-9]+", "", x[1]))
    ##x <- unlist(strsplit(loc2$match_address, ","))
    ##newstreet2 <- trimws(sub("^[0-9]+", "", x[1]))
 ## }
  if (street != newstreet1 && street != newstreet2) {
    print(paste("failure 2", street, newstreet1, newstreet2, 
                sep=" : "))
    return(data.frame(
      status="failmatch",
      match_address=loc1$match_address,
      lat=NA,
      long=NA,
      tract=NA,
      block=NA,
      distance=NA,
      stringsAsFactors = FALSE
    ))
  } else if (street != newstreet1 || street != newstreet2) {
    # Find good address and borrow zip to fix bad address
    if (street == newstreet1){
      print("street == newstreet1")
      zip <- last(unlist(str_split(loc1$match_address," ")))
      loc2 <- Census_decoder(paste(adr2, street), city, zip=zip)
    } else {
      print("street == newstreet2")
      zip <- last(unlist(str_split(loc2$match_address," ")))
      loc1 <- Census_decoder(paste(adr1, street), city, zip=zip)
    }
  }
  if (is.na(loc1$match_address) || is.na(loc2$match_address)) {
    print(paste("failure 3", street, newstreet1, newstreet2, 
                sep=" : "))
    return(data.frame(
      status="failmatch2",
      match_address=loc1$match_address,
      lat=NA,
      long=NA,
      tract=NA,
      block=NA,
      distance=NA,
      stringsAsFactors = FALSE
    ))
  }
  
  #   Look at distance between results
  
  distance <- sqrt((loc1[3] - loc2[3])**2 + 
                   (loc1[4] - loc2[4])**2)* 69 # approx in miles
  #print(paste("distance =", distance))
  #print("=============")
  
  #   Average coordinates and check tract and block match
  
  lat <- (loc1[3] + loc2[3])/2
  long <- (loc1[4] + loc2[4])/2
  
  return(data.frame(
    status="success",
    match_address=loc1$match_address,
    lat=lat,
    long=long,
    tract=loc1[5],
    block=loc1[6],
    distance=distance,
    stringsAsFactors = FALSE
  ))
  
}
```

```{r do work}


#####################################
##    spin through data geocoding
#####################################

newlymatched <- data.frame(
  old_address=character(),
  match_address=character(),
  lat=double(),
  long=double(),
  tract=character(),
  block=character(),
  distance=double(),
  stringsAsFactors = FALSE
)
newerunmatched <- data.frame(
  old_address=character(),
  match_address=character(),
  lat=double(),
  long=double(),
  tract=character(),
  block=character(),
  distance=double(),
  stringsAsFactors = FALSE
)

#for (i in 4:nrow(newunmatched)) {
for (i in 5:5) {
  print(paste("--->",i,lastunmatched[i,1]))
  if (grepl("UNK ", lastunmatched[i,1])){next}
  oldaddress <- lastunmatched[i,1]
  beat <- lastunmatched[i,2]
  latlong <- getlatlong(oldaddress, beat)
  if (latlong$status=="success") {
    print(paste("=======final=======",latlong[1,]))
    latlong <- cbind(oldaddress, latlong)
    names(latlong)[names(latlong)=="lat.1"] <- "distance"
    newlymatched <- rbind(newlymatched, latlong)
    newlymatched[,1] <- as.character(newlymatched[,1])
  } else {
    latlong <- cbind(oldaddress, latlong)
    names(latlong)[names(latlong)=="lat.1"] <- "distance"
    newerunmatched <- rbind(newerunmatched, latlong)
    newerunmatched[,1] <- as.character(newerunmatched[,1])
  }
}
#newlymatched[,1] <- as.character(newlymatched[,1])
#names(newlymatched)[names(newlymatched)=="unmatched[i, ]"] <- "oldaddress"

saveRDS(newlymatched, "~/Dropbox/CrimeStats/CensusGeoTable.rds")
saveRDS(newerunmatched, "~/Dropbox/CrimeStats/UnCodedData.rds")

```
## pull out still unmatched addresses and categorize why matches failed

Only do this once - code to eliminate this step has been added 
for future use above.

```{r further mismatches}
newunmatched <- newlymatched %>%
  select(oldaddress) %>%
  rename(Address=oldaddress) %>%
  setdiff(unmatched, .)

for (i in 3:3) {
  print(paste("--->",i,newunmatched[i,]))
  latlong <- getlatlong(newunmatched[i,])
  if (latlong$status=="success") {
    print(paste("--final--",latlong[1,]))
  } 
}


####   repairs to be propagated upstream

lastunmatched$Address <- str_replace(lastunmatched$Address, "FWY FWY", "FWY")
lastunmatched$Address <- str_replace(lastunmatched$Address, "FWY SER", "FWY")
lastunmatched$Address <- str_replace(lastunmatched$Address, "GREENBRIAR DR", "GREENBRIAR ST")
lastunmatched$Address <- str_replace(lastunmatched$Address, "GREENWICH PL ", "GREENWICH PLACE DR ")

```

Greenbriar Dr -> Greenbriar St

